Optimal Decomposition-Recombination Plans for 2D Well-Constrained Graphs

### 2014-12-04 doc/GMP2015/s01_introduction.tex
s01_introduction.tex edited online with Bitbucket

Two key observations serve as the motivations for this paper:
As constraint systems, 2D sesamacs involve multiple types of 
well-studied geometric constraint systems: so-called
{\it bar-joint} systems (Examples 1,2 above), {\it multibody-pin} systems (Example 4,5) or {\it pinned-line incidence} systems (Example 3).  
All of these systems have highly efficient combinatorial algorithms (pebble-game \cite{XX}, or equivalently, simplified network flow \cite{XX}) 
for locating maximal, generically rigid components \cite{XX}.

Recursive decompositions of 2D sesamacs into rigid subsystems is important in order to understand or design rigidity, flexes and distribution 
of external stresses  -- at all scales.

>>>>

Two key observations serve as the motivations for this paper:
As constraint systems, 2D sesamacs  are  well-studied: so-called
{\it bar-joint} systems (Examples 1,2 above), {\it multibody-pin} systems (Example 4,5) or {\it pinned-line incidence} systems (Example 3).  
All of these systems have highly efficient combinatorial algorithms (pebble-game \cite{XX}, or equivalently, simplified network flow \cite{XX}) 
for locating maximal, generically rigid components \cite{XX}.

Especially due to their recursive structure, recursive decompositions of 2D sesamacs 
is imperative
in order to understand or design rigidity, flexes and distribution 
of external stresses  -- at all scales. In fact, this has been studied combinatorially as the Decomposition-Recombination (DR)
-planning problem \cite{XX}.  
In particular, since many different such decompositions typically exist, is to ensure that any system is decomposed into a minimal set 
of maximal rigid proper subsystems  
such that they can be recombined efficiently
